Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-04-03 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Add mass loss files, plots, script, update latex, remove old figures

\begin{figure}[p]
  \centering
  \includegraphics[width=4.5in]{../Figures/Fig12}\\
  \includegraphics[width=4.5in]{../Figures/Fig13}\\
  \caption[Mass loss versus time for the gasoline and foam fueled fires]{Mass loss versus time for the gasoline and foam fueled fires.}
  \label{Mass}
\end{figure}

@@

The thermocouple arrangement for these experiments, only had one vertical array of thermocouples.  The thermocouples were positioned between the two vertical arrays of heat flux gauges as shown in Figure~\ref{Instrumented_GB_Wall}  As a means of ensuring contact between the gypsum wallboard and the thermocouple, the thermocouples were installed by pulling the positive and negative wires through holes drilled on the horizontal centerline between the heat flux gauges and positioning the bead of the thermocouple in a slit in the paper face made with a razor blade.  A thermocouple installed in this manner shown in Figure {\bf fig reference}

@@

% \begin{figure}
% 	\centering
% 	\includegraphics[width=\textwidth]{../Figures/Instrumented_GB_Wall}\\
% 	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall. Two vertical arrays of total heat flux gauges and thermocouples were installed along the centerline of the burner and along the right edge of the burner.}
% 	\label{Instrumented_GB_Wall}
% \end{figure}

>>>>

\begin{figure}[p]
  \centering
  \includegraphics[width=4.5in]{../Figures/ML_GAS}\\
  \includegraphics[width=4.5in]{../Figures/ML_PUF}\\
  \caption[Mass loss versus time for the gasoline and foam fueled fires]{Mass loss versus time for the gasoline and foam fueled fires.}
  \label{Mass}
\end{figure}

@@

The thermocouple arrangement for these experiments had one vertical array of thermocouples installed on the wall.  The thermocouples were centered between the two vertical arrays of heat flux gauges as shown in Figure~\ref{Instrumented_GB_Wall}.  As a means of ensuring contact between the gypsum wallboard and the thermocouple, the thermocouples were installed by pulling the positive and negative wires through holes drilled through the gypsum wallboard and positioning the bead of the thermocouple in a slit in the paper face made with a razor blade.  A thermocouple installed in this manner shown in Figure~\ref{IWGB_TC_Slit}.

@@

 \begin{figure}
 	\centering
 	\includegraphics[width=\textwidth]{../Figures/IWGB_TC_Slit}\\
 	\caption[Photograph of a thermocouple embedded in the gypsum wallboard]{Photograph of a nominal 0.5 mm thermocouple bead embedded in the gypsum wallboard.}
 	\label{IWGB_TC_Slit}
 \end{figure}
